---
title: "Regus2014 Data Analysis"
author: "dned"
date: "09/09/2014"
output: 
    html_document:
        keep_md: true
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(tidy = FALSE, fig.height=4, echo=FALSE)
options(stringsAsFactors = FALSE)
library(dplyr)
library(ggplot2)
```


Downloaded the data from Regus2014, pasted into Google Spreadsheets, and saved as a tsv.

Holy shit, the population data is in `1.86 X 10 6` format, gross. Did some regex to make it sane: `1.86e6`. One line, "Winter 509 14x2 0 2 6.00  X 10 6 9. 5  X 10 6", had an issue with the last value, "9. 5". I assumed there was a zero missing, and corrected that.

Reading the data in and taking a peak at it:

```{r}
setwd("~/Dropbox/gradschool/Regus2014/data")
nodCulturing.df <- read.csv("Regus2014_TableS6.tsv", header= TRUE, sep="\t")
```

```{r}
head(nodCulturing.df)
```

Do the two experiments have roughly the same distribution of nodule counts?
```{r}
ggplot(nodCulturing.df, aes(x=Experiment, y=PopEffStrain)) + geom_violin(fill="darkgrey")
```

