---
title: "Wilczek2014 analysis"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(tidy=FALSE, fig.height = 4, message=FALSE)
```

Reading the data in. Data was processed in `dataWrangle.Rmd`
```{r}
setwd("~/Dropbox/gradschool/paperAnalysis/Wilczek2014/data/")
load("sd01_fitnessLong.Rdata")
```

Since a lot of things choke with NAs, I'm going to remove them from YearCollected. This removes the lines that I don't have date for when they were collected. Kind of important if looking at lines that are different through time.

```{r}
fitness.df <- fitness.df[ complete.cases(fitness.df["YearCollected"]),]
```

Christ, having "Autumn" instead of Fall is annoying
```{r}
fitness.df$Season <- gsub("Autumn", "Fall", fitness.df$Season)
```



### Making old / modern factor

Can I partition the pops into a simple old / modern division?
```{r}
ggplot(fitness.df, aes(x=Lat, y=YearCollected)) + geom_point() + geom_hline( y=1970) + ggtitle("Potential partitioning of historical populations")
```

It looks there's a gap from ~1965 to ~1975, so partitioning at 1970 looks like a good time.

Another thing to do would be look at annual trends in temperature, and pick a spot where there is a change in the rate of increase as a means of deciding which populations belong to one of the two groups. But I'll leave that as an excercise for the reader.

```{r}
fitness.df$HistPop <- 1
fitness.df[fitness.df$YearCollected > 1970, "HistPop" ] <- "modern"
fitness.df[fitness.df$YearCollected < 1970, "HistPop" ] <- "old"
```


## Fitness in each region

Let's compare the fitness of the old and modern pops in Halle (51.4833° N, 11.9667° E) in Fall
```{r, message=FALSE}
fallHalle <- fitness.df %>% filter(Season == "Fall", Location == "Halle")
halleFitness <-ggplot(fallHalle, 
       aes(x = Lat, y= Fitness)) +
  geom_point(alpha=.5) + geom_smooth(method="loess") +
  geom_vline(x=51.488) +
  ggtitle("Fitness at Halle in Autumn")
halleFitness

# Now with Facets reflect the population
halleFitness + facet_grid(HistPop ~ .)
```


```{r}

```


