---
title: "Wilczek2014 analysis"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
knitr::opts_chunk$set(tidy=FALSE, fig.height = 4)
```

### Stuff to do
- use reshape to make the data long (Fitness in each site turned into a factor and one column of fitness)

reading the data in
```{r}
setwd("~/Dropbox/gradschool/paperAnalysis/Wilczek2014/")
datasetS1 <- read.csv("pnas.1406314111.sd01.csv")
```

let's see if lat or lon predicts differences in fitness

Working with the fitness in Halle, 51.4833° N, 11.9667° E

```{r}
summary(lm(datasetS1$Fitness.in.Halle.Autumn ~ datasetS1$Latitude.of.Origin))
plot(datasetS1$Fitness.in.Halle.Autumn ~ datasetS1$Latitude.of.Origin)


halleFitness <-ggplot(datasetS1, 
       aes(x = Latitude.of.Origin, y= Fitness.in.Halle.Autumn)) +
  geom_point(alpha=.5) + geom_smooth(method="loess") +
  geom_vline(x=51.488) +
  ggtitle("Fitness at Halle in Autumn")
halleFitness

# Now with Facets
halleFitness + facet_grid(Time.period ~ .)

```


## Fig 2
instead of box plots, I want violin plots. Jerks didn't give m a table of how they binned the different accessions into a region. 

```{r}
# 2A
# ggplot(datasetS1, aes(x=))
```




## Recreating fig 3
I really didn't like how they were showing trends in plots that looked like a bunch of garbage

Is there a way I partition the data into more modern pops, and then older pops, to compare historical differences. From the plot of `Likely.Year.Collected ~ Lattitude.of.Origin`, it looks there's a gap from ~1965 to ~1975, so partitioning at 1970 looks like a good time.

```{r}
ggplot(datasetS1, aes(x=Latitude.of.Origin, y=Likely.Year.Collected)) + geom_point() + geom_hline( y=1970) + ggtitle("Potential partitioning of historical populations")
```

Another thing to do would be look at annual trends in temperature, and pick a spot where there is a change in the rate of increase as a means of deciding which populations belong to one of the two groups.

## Looking at year collected and the latitude

```{r}
ggplot(datasetS1, aes(x=Latitude.of.Origin, y=Likely.Year.Collected)) + geom_point()
```

Lat 45 is only present in 1960 and previous; 50 could be over represented by earlier collected dates. 


## 
