---
title: "Exploratory Analysis"
author: "Derek Nedveck"
date: "11/17/2014"
output: html_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(tidy = FALSE, fig.height = 4)
```


```{r, message=FALSE}
library(dplyr)
library(ggplot2)
```


Taking a peak

```{r}
setwd("../data")
jsg.df <- read.csv("CfE2_data.csv", header = TRUE)
```

## Data

This experiments were looking at fitness, so the response variables are going to be dealing with number of seed pods per plant (`seed.pods`), number of pods collected to count seeds (`pods.counted`), number of seeds in these pods (`seeds.counted`), and the average seed weight (`avg.seed.weight`)

## Plots

Looking at the distributions of the fitness variables:
```{r}
ggplot(jsg.df, aes(x = seed.pods)) + geom_histogram()
ggplot(jsg.df, aes(x = pods.counted)) + geom_histogram()
ggplot(jsg.df, aes(x = seeds.counted)) + geom_histogram()
ggplot(jsg.df, aes(x = avg.seed.weight)) + geom_histogram()
```

## let's see how things are correlated

```{r}
plot(seed.pods ~ region,data = jsg.df)
ggplot(jsg.df, aes(x = seed.pods, fill = region)) + geom_histogram()
```

