---
title: "Adding and Processing Barrett2014 Data"
author: "Derek Nedveck"
date: "11/19/2014"
output: html_document
---

This report shows how I am adding columns to the data frame to facilitate some later data analysis, as well as setting up the data.frame to be exported as an R object to be used in some classroom data analysis. 

## Bring in Data
```{r}
# data from the paper
barrett.df <- read.csv("Barrett2014.csv")
# factors I created using info from the metadata
bact.df <- read.csv("bactTreatmentVars.csv")
```

### doing some data.frame maintenence

```{r}
str(barrett.df)
# bact.trt, nodulation, treat.no should be factors
barrett.df$bact.trt <- as.factor(barrett.df$bact.trt)
barrett.df$nodulation <- as.factor(barrett.df$nodulation)
barrett.df$treat.no <- as.factor(barrett.df$treat.no)
# Number doesn't seem to add any information (it is correlated with bac.trt)
#  also not mentioned in the metadata, so I am removing it
barrett.df$Number <- NULL
str(barrett.df)
```

```{r}
str(bact.df)
# bact.trt and bact.div should be factors
bact.df$bact.trt <- as.factor(bact.df$bact.trt)
bact.df$bact.div <- as.factor(bact.df$bact.div)
str(bact.df)
```


### Merging the dataframes together 

```{r}
barrett.df <- merge(x = barrett.df, y = bact.df, by.x= "bact.trt", by.y = "bact.trt")
```

Since `treat.no` is covered in `rhiz.strain` (except with more information), I am removing this from the data frame
```{r}
barrett.df$treat.no <- NULL
```

## Saving data
```{r}
write.table(x = barrett.df, file = "barrett2014_processed.csv", sep = ",",
            quote = FALSE, row.names = FALSE )
save(barrett.df, file = "barret.df.Rdata")
```

